Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-11-18 paper/main.tex
restructure quotes aPPA vs pPPA

% title has to be < 110 chars incl. spaces
%  at the moment 109 Chars
\title{Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description}

@@

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
regions.
% PPA
The ``parahippocampal place area'' is classically considered to be a higher
visual area as increased hemodynamic activity in the PPA correlates/is
correlated with the perception of static pictures of landscapes (or landmarks)
compared to pictures of faces or objects.
% What we do
In the current study, we exploratorily tested if spatial information embedded in
the audio-description of a Hollywood movie (i.e. the movie's soundtrack with an
additional narrator) the audio-visual movie can be used to isolate the PPA on a
group average level and in individual subjects.
%
We use publicly available functional magnetic resonance imaging data
(studyforrest.org) to build canonical general linear model (GLM) $t$-contrasts
and compare current results to results that we gained from a dedicated visual
localizer experiment conducted with the same 14 participants.
% compare to visual localizer experiment group results
On a group average level, our results show significantly increased activation in
the PPA but restricted to its anterior part [as well as in the retrosplenial and
lateral occipital cortex] of both hemispheres.
% individual results
On an individual level, results show significant bilateral clusters in the
anterior PPA of nine subjects and significant unilateral clusters in two
subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of auditorily presented spatial
information.
% conclusion: PPA has subregions
Lastly, our results provides further evidence that the PPA can be divided into
functional subregions.\todo{kinda bold statements; this depends on the data \&
discussion}\end{abstract}

@@

% intro
Notably, results of the AO contrasts consistently yielded significant clusters
spatially constrained to the anterior part of the PPA group overlap (and
anterior part of significant clusters of the AV contrasts).
% intro to connectivity and object gradient
Previous studies suggest that posterior and anterior part of the PPA show both a
difference in connectivity profiles \citep{baldassano2013differential} and a
gradient in sensitivity to scene and abstract object stimuli
\citep{arcaro2009retinotopic, aminoff2007parahippocampal,
baldassano2013differential}.
% high level summary: posterior

\paragraph{posterior: connectivity \& object sensitivity}

% Baldassano (2013): Our description of posterior PPA is in fact similar to the
% original proposal of Aguirre et al. for a “lingual landmark area” (LLA),
% slightly posterior to PPA, which was “specialized for the perception of visual
% stimuli with orienting value” (Aguirre et al., 1998) and carried out bottom-up
% perceptual analysis to recognize locations or landmarks (Cant and Goodale,
% 2007; Epstein et al., 1999). Although the LLA is no longer identified as an
% independent region from PPA in current studies, it is possible that the
% posterior portion of PPA corresponds to the properties of the proposed LLA,
% offering an explanation for why this region was localized more posteriorly
% than the full PPA.

% connectivity
The posterior PPA is more functionally connected to the occipital visual cortex,
including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
\citep{baldassano2013differential}.
% LOC and TOS
[These regions have well-defined retinotopic maps (Arcaro et al., 2009; Nasr et
al., 2011), and are associated with the perception of low-level visual features
and object shape \citep{baldassano2013differential}.]
% object sensitivity
Previous work has hinted that posterior PPA is more responsive to both simple
visual textures and (abstract) objects \citep{arcaro2009retinotopic,
baldassano2013differential}.
%
The posterior portion of PPA responded about four times as strongly to a
flickering checker-board stimulus compared to an anterior portion, and that the
response to objects was greater than the response to scrambled images only in
the posterior portion => posterior PPA may be more visually responsive than
anterior PPA \citep{arcaro2009retinotopic}.
% in summary: posterior
In summary, the posterior PPA is more concerned with perception of low-level
visual features and object shape.

\paragraph{anterior: connectivity \& (non) contextual sensitivity}

The anterior PPA is more functionally connected to the RSC and parietal cortices
(caudal inferior parietal lobe; cIPL)[, medial PFC, and the lateral surface of
the anterior temporal lobe] \citep{baldassano2013differential}.
% default mode network
[anterior PPA is also more strongly connected to regions in the default mode
network (including the parieto-medial temporal pathway).
\citep{baldassano2013differential}.]
% DMN details
The set of regions connected more strongly to anterior PPA is strikingly similar
to the Default Mode Network (DMN) (Buckner et al., 2008; Fox et al., 2005;
Raichle et al., 2001), which is known to include the parahippocampal region (the
only portions of the DMN that do not show differential connectivity to anterior
PPA in our data are the rostral portion of the posterior cingulate cortex (PCC)
and the superior frontal cortex) \citep{baldassano2013differential}.
% DMN and contextual association
DMN has been implicated in a large number of internally-focused tasks, one of
its key roles involves autobiographical memory (Buckner et al., 2008).  Models
of recognition memory have previously identified parahippocampal cortex as
primarily encoding spatial context information (Eichenbaum et al., 2007)
\citep{baldassano2013differential}.
% Baldassano regarding Aminoff
Data from \citep{aminoff2007parahippocampal} has suggested that an anterior
portion of PPA may be involved in recall based on spatial context
\citep{baldassano2013differential}.
%
Given anterior PPA's connectivity with the DMN.Our results are consistent with
anterior PPA playing a more central role in memory than posterior PPA
\citep{baldassano2013differential}.

% object sensitivity
The anterior PPA is less visually responsive to both scenes and objects, with
notably low sensitivity to abstract object stimuli, and more involved in memory
and global contextual processing \todo{quotes???}
%
The fact that anterior PPA had a lower sensitivity to our abstract object
stimuli does not necessarily imply that this region does not use object
information \citep{baldassano2013differential}.
%
Previous work has shown that PPA responds to objects that have spatial
associations (Aminoff et al., 2007), are space-defining (Mullally and Maguire,
2011), and are navigationally-relevant (Janzen and Van Turennout, 2004).

\paragraph{conclusion: subregions}

\todo[inline]{re-read Baldassano (2013)}

\todo[inline]{discussing PPA in context of contextual associations might provide
a smooth transition to (possibly) following discussion of RSC}

% Aminoff
\citep{aminoff2013role} in general (s. also \citep{aminoff2007parahippocampal}:
processing of strong, long-term, contextual associations elicits activity within
the PHC, as well as the RSC (which includes regions of the retrosplenial cortex,
extending into the posterior cingulate cortex, and the precuneus), the medial
prefrontal cortex (MPFC), and the transverse occipital sulcus (TOS) (Figure 2)
[2,3,59–67].
% Aminoff: contextual associations in anterior vs. posterior
\citep{aminoff2007parahippocampal} propose that a subregion of the posterior PHC
is particularly optimized to process spatially organized contextual
associations, whereas more anterior regions of the PHC are optimized to process
contextual associations in other, non-spatial domains.
% posterior PPA for visual visual associative information
Spatial contextual associations are a dominant property of places and scenes,
and thus scenes consistently activate this posterior subregion of the PHC (e.g.,
PPA; Epstein, 1998).
%
We do not argue that the PHC is not sensitive to spaces, places, and spatial
information, but rather that it is sensitive to spatial stimuli because of the
associative information (space-related associations) that such stimuli evoke.

% Aminoff regarding contextual processing in the PHC and beyond
\citep{aminoff2007parahippocampal}: We compared contextual processing of objects
that are strongly related to a specific place (e.g., an oven is found in a
kitchen) with contextual processing of objects that are highly associated with a
context but not a specific place (e.g., a birthday cake is found at a birthday
party, but the party can take place anywhere, at home, in a restaurant, at a
park).
% method
Activity elicited by these two types of contextual objects was compared with the
activity elicited for objects that were only weakly associated with many
contexts (e.g., a lamp).
% results
Differential activity was found in the PHC and the RSC, replicating the previous
findings (Bar \& Aminoff, 2003, The parahippocampal\dots).
% results 2
\citep{aminoff2007parahippocampal} Activity within the PHC, however, was
distributed along an anterior–posterior axis, with activity related to spatial
contexts focused in the posterior part of the PHC and activity evoked by
non-spatial contexts focused in the more anterior part of the PHC (Bar \&
Aminoff, 2003, Cortical analysis of visual context; Aminoff et al., 2007, The
parahippocampal cortex mediates spatial and nonspatial associations).

% Baldassano (2013): PPA subregions
Data suggest that PPA might contain identifiable subregions, but subregions
should not be considered as completely independent modules. Both subregions
activate selectively to scenes, implying that these subregions cooperate to
build a complete representation of a scene [that sentence is taken from
\citep{baldassano2013differential}].
% Baldassano (2013): conclusion
Their distinct connectivity properties, however, suggests that each may be
involved in specific aspects of visual and cognitive processing involved in the
overarching goal of scene understanding.
%
These types of responses require spatial memory and cannot be based purely on
visual features like object shape.
%
If anterior PPA is involved in processing spatial context, then space-defining
or navigationally-relevant objects could activate anterior PPA more strongly
than our abstract objects, which were unfamiliar and provided no sense of
context or orientation.
%
Further experiments will be required to determine what type of object-related
information is used in this region.

>>>>

% title has to be < 110 chars incl. spaces
%  at the moment 109 Chars
\title{Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description}

@@

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
The ``parahippocampal place area'' is classically considered to be a higher
visual area as increased hemodynamic activity in the PPA correlates/is
correlated with the perception of static pictures of landscapes (or landmarks)
compared to pictures of faces or objects.
% What we do
In the current study, we exploratorily tested if spatial information embedded in
the audio-description of a Hollywood movie (i.e. the movie's soundtrack with an
additional narrator) the audio-visual movie can be used to isolate the PPA on a
group average level and in individual subjects.
%
We use publicly available functional magnetic resonance imaging data
(studyforrest.org) to build canonical general linear model (GLM) $t$-contrasts
and compare current results to results that we gained from a dedicated visual
localizer experiment conducted with the same 14 participants.
% compare to visual localizer experiment group results
On a group average level, our results show significantly increased activation in
the PPA but restricted to its anterior part [as well as in the retrosplenial and
lateral occipital cortex] of both hemispheres.
% individual results
On an individual level, results show significant bilateral clusters in the
anterior PPA of nine subjects and significant unilateral clusters in two
subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of auditorily presented spatial
information.
% conclusion: PPA has subregions
Lastly, our results provides further evidence that the PPA can be divided into
functional subregions.\todo{kinda bold statements; this depends on the data \&
discussion}\end{abstract}

@@

% intro
Results of the AO contrasts consistently yielded significant clusters
spatially constrained to the anterior part of the PPA group overlap (and
anterior part of significant clusters of the AV contrasts).
% intro to connectivity and object gradient
[kind of complete overview of (references):] Previous studies suggest that
posterior and anterior part of the PPA show differences in
% connectivity
a) connectivity profiles \citep{baldassano2013differential, baldassano2016two}[+
Nasr et al., 2013; Silson et al., 2016a],
% scenes vs abstract objects
b) a gradient in sensitivity scene and abstract object stimuli
\citep{arcaro2009retinotopic, aminoff2007parahippocampal,
baldassano2013differential},
% low-level scene features
c) differences in response to low-level scene features [Nasr et al., 2014;
Silson et al., 2015; Baldassano et al., 2016a,b; Watson et al., 2016],
% high-level scene features
d) high-level scene features [Park et al., 2014; Aminoff and Tarr, 2015; Linsley
and Macevoy, 2015; Marchette et al., 2015],
% TMS
e) stimulation studies [Rafique et al., 2015] \citep{baldassano2016two}

\paragraph{posterior PPA (pPPA)}

% connectivity
The posterior PPA is more [strongly] functionally connected to the occipital
visual cortex, including lateral occipital cortex (LOC) and transverse occipital
sulcus (TOS) \citep{baldassano2013differential, baldassano2016two}.
% LOC and TOS
[These regions have well-defined retinotopic maps (Arcaro et al., 2009; Nasr et
al., 2011), and are associated with the perception of low-level visual features
and object shape \citep{baldassano2013differential}.]

%
Increased activity within the pPHC during viewing of scenes relative to objects
has been suggested to reflect regional specialization for visuospatial processes
related to the extraction of scene layout information [Epstein,
2008]\citep{baumann2016functional}.

% high-level visual features
Higher-level visual features also drive response patterns in these regions
[Bryan et al., 2016]. They are hypothesized to be involved in extracting visual
environmental features that can be used for navigation [Marchette et al., 2015;
Julian et al., 2016; Kamps et al., 2016]. However, neither OPA nor posterior PPA
show reliable familiarity effects [Epstein et al., 2007b; see further discussion
below]\citep{baldassano2016two}.
%
The idea that the pPHC serves a dedicated role in visuospatial processing is
further supported by studies showing that this brain region is sensitive to
changes in basic visuospatial properties such as the shape and spatial frequency
of abstract geometric objects and layouts [Rajimehr et al., 2011; Zeidman et
al., 2012]\citep{baumann2016functional}.

% object sensitivity
The pPPA is more responsive to both simple visual textures and (abstract)
objects \citep{arcaro2009retinotopic, baldassano2013differential}:
%
The pPPA responded about four times as strongly to a
flickering checker-board stimulus compared to an anterior portion
\citep{arcaro2009retinotopic}.
%
The response to objects was greater than the
response to scrambled images only in the posterior portion
\citep{arcaro2009retinotopic}.

% low-level features
OPA and pPPA have been shown to be closely related to the visual content of a
stimulus. Even low-level manipulations of spatial frequency [Rajimehr et al.,
2011; Kauffmann et al., 2015; Watson et al., 2016] or rectilinearity [Nasr et
al., 2014] can drive responses in these regions \citep{baldassano2016two}.

% baumann2016functionl
We observed that pPHC is more strongly modulated bilaterally by the visual
properties of the stimulus material (as evidenced by strong responses in the
picture-scene conditions and no significant response in the word-object
conditions)\citep{baumann2016functional}.
%
Our current study [and findings of Baldassano et al. (2013)] suggest that the
functional topographic segregation of the PHC is underpinned by corresponding
segregated connectivity patterns. Findings are consistent with a model of
parahippocampal function in which visual information is projected from occipital
and temporal areas to the pPHC [Libby et al., 2012], where encoding of
visuospatial information takes place (a process that is computationally more
demanding for complex stimuli such as scenes than for simple ones such as
objects; Chai et al., 2010)\citep{baumann2016functional}.

\paragraph{posterior network}

% baldassano2016two
The 1st (posterior) network [of two networks] includes
pPPA and OPA/TOS. pPPA (retinotopic maps PHC1 \& PHC2) and OPA/TOS contain
retinotopic maps and are not strongly coupled to the hippocampus at rest
\citep{baldassano2016two}.

% baldassano20160two: Neurosynth meta-analysis
\citep{baldassano2016two}'s ``meta-analysis'' using Neurosynth: we compare the
query ``scene'' (47 studies) with the query ``episodic memory, navigation, past
future'' (125 studie).
%
Results: voxels significant only in the scene meta-analysis were concentrated in
the posterior network (66\% in posterior network, 18\% in anterior, 16\% in
other) % baldassano2016two: meta-analysis
\citep{baldassano2016two} Voxels significant in both the scene and
memory/navigation meta-analyses tended to fall near the border between the two
networks and divided approximately equally among them (44\% posterior, 53\%
anterior, 4\% other).
%
\citep{baldassano2016two} Voxels significant only in the memory/navigation
meta-analysis were spread more widely across the cortex, but were concentrated
more in the anterior than the posterior network (16\% posterior, 42\% anterior,
42\% other).

% interpretation
Interpretation: visual scene activations tend to be posterior to the memory
activations along the parahippocampal gyrus. [The transition point corresponds
almost exactly to the division between our two networks. Dorsally, we also
observe a separation between the reverse inference maps, with scene and memory
activations falling into our two separate networks \citep{baldassano2016two}.]

\paragraph{anterior PPA (aPPA)}

The specific properties of aPPA have been less well studied, since it was not
recognized as a separate region within the PPA until recently
\citep{baldassano2016two}.

% anterior PPA
The anterior PPA is more [strongly] functionally connected to the RSC and
parietal cortices (caudal inferior parietal lobe; cIPL)[, medial PFC, and the
lateral surface of the anterior temporal lobe]
\citep{baldassano2013differential, baldassano2016two}.

% object sensitivity
The aPPA is less visually responsive to both scenes\todo{check their paradigm \&
result section} and objects, with notably low sensitivity to abstract object
stimuli \citep{baldassano2013differential}.
%
Results suggest that aPPA may be more concerned with these types of spatial and
non-object-based scene properties [= global scene properties such as spatial
expanse] than posterior PPA \citep{baldassano2013differential}\todo{check if
quoted correctly}.

\citep{baldassano2016two} The aPPA is
% category
a) driven more by high-level category information than by spatial frequency
content [Watson et al., 2016],
% locations
b) to represent real-world locations (even from perceptually distinct views)[
Marchette et al., 2015],
% associations
c) to encode object co-occurrences [Aminoff and Tarr, 2015], and
% scene size
d) to represent real-world physical scene size [Park et al., 2014]
\citep{baldassano2016two}.
% spaciousness
Its representation of scene spaciousness draws on prior knowledge about the
typical size of different scene categories, since it is affected by the presence
of diagnostic objects [Linsley and Macevoy, 2015]\citep{baldassano2016two}.

\paragraph{anterior network}

% baldassano2016two's networks
\citep{baldassano2016two} The anterior network (the 2nd of two networks)
consists of the caudal inferior parietal lobule (cIPL), RSC, and aPPA, which
connect to the hippocampus (especially anterior hippocampus). These regions are
implicated in both visual and nonvisual tasks, including episodic memory and
navigation] \citep{baldassano2016two}.
% baldassano2016connectivity
The anterior network [that includes aPPA] exhibits much higher resting-state
hippocampal coupling (especially to anterior hippocampus), suggesting that
memory- and navigation-related functions are primarily restricted to the
anterior network \citep{baldassano2016two}.

% The memory and navigational network
The network of parahippocampal, retrosplenial, and posterior parietal regions
that we identify has been emerged independently in many different fields of
neuroimaging, outside of scene perception.
%
Meta-analyses of internally directed tasks, such as theory of mind,
autobiographical memory, and prospection, have identified this as a core,
reoccurring network [Spreng et al., 2009; Kim,2010; Yeo et al., 2015 (component
C10 of ?)]. It comprises a subset of the broader default mode regions, but
functional and anatomical evidence suggests that it is a distinct, coherent
subnetwork [Andrews-Hanna et al., 2010, 2014; Yeo et al.,
2011]\citep{baldassano2016two}.
%
The broad set of tasks that recruit this network have been summarized in various
ways, such as ``scene construction'' (Hassabis and Maguire, 2007), ``mnemonic
scene construction'' [Andrews-Hanna et al., 2010], ``long-timescale
integration'' [Hasson et al., 2015], or ``relational processing'' [Eichenbaum
and Cohen, 2014].
%
A review of memory studies referred to this network as the posterior medial
memory system, and proposed that it is involved in any task requiring
``situation models'' relating entities, actions, and outcomes [Ranganath and
Ritchey, 2012]\citep{baldassano2016two}.

% hippocampus
The network has strong functional connections to the hippocampus, which has been
implicated in a broad set of cognitive tasks involving ``cognitive maps'' for
organizing declarative memories, spatial routes, and even social dimensions
[Eichenbaum and Cohen, 2014; Schiller et al., 2015]. During perception, the
hippocampus binds together visual elements of an image [Olsen et al., 2012;
Warren et al., 2012; Zeidman et al., 2015], which is especially important for
scene stimuli [Lee et al., 2005a,b; Graham et al., 2006; Hodgetts et al., 2016].
The hippocamppus then stores this representation into long-term memory [Ryan and
Cohen, 2004]\citep{baldassano2016two}.
%
Our results suggest that only the anterior scene regions interface directly with
the hippocampus, potentially enabling the construction of hippocampal
environmental representations, and retrieval of relevant memories and
navigational information for a presented or imagined
scene\citep{baldassano2016two}.

\paragraph{conclusion \& interpetation: subregions}

% conclusion by Baldassano (2013): PPA subregions
Data suggest that PPA might contain identifiable subregions, but subregions
should not be considered as completely independent modules.
%
Both subregions activate selectively to scenes, implying that these subregions
cooperate to build a complete representation of a scene
\citep{baldassano2013differential}.

We do not argue that the PHC is not sensitive to spaces, places, and spatial
information, but rather that it is sensitive to spatial stimuli because of the
associative information (space-related associations) that such stimuli evoke
\citep{aminoff2013role}.
% posterior PPA for visual visual associative information
Spatial contextual associations are a dominant property of places and scenes,
and thus scenes consistently activate this posterior subregion of the PHC (e.g.,
PPA; epstein1998ppa)\citep{aminoff2013role}.

% baldassano2013: functional contrast
The fact that aPPA had a lower sensitivity to our abstract object stimuli does
not necessarily imply that this region does not use object information
\citep{baldassano2013differential}.
% baldassano2013: connectivity
Their distinct connectivity properties, however, suggests that each may be
involved in specific aspects of visual and cognitive processing involved in the
overarching goal of scene understanding.
%
Previous work has shown that PPA responds to objects that have spatial
associations [Aminoff et al., 2007], are space-defining [Mullally and Maguire,
2011], and are navigationally-relevant [Janzen and Van Turennout, 2004]. These
types of responses require spatial memory and cannot be based purely on visual
features like object shape.
%
If anterior PPA is involved in processing spatial context, then space-defining
or navigationally-relevant objects could activate anterior PPA more strongly
than our abstract objects, which were unfamiliar and provided no sense of
context or orientation \citep{baldassano2013differential}. Further experiments
will be required to determine what type of object-related information is used in
this region \citep{baldassano2013differential}.

% baldassano2016two
\citep{baldassano2016two}: We propose that scene processing is fundamentally
divided into two collaborating but distinct networks
%
One is focused on the visual features of a scene image. The other is related to
contextual retrieval and navigation.
%
Under this framework, scene perception is less the function of a unified set of
distributed neural machinery and more of ``an ongoing dialogue between the
material and symbolic aspects of the past and the continuously unfolding
present'' (Baker, 2012, in The Word Hoard).
%
\citep{baldassano2016two} with respect to natural scene perception: one can
imagine at least two separable functions:
%
1) processing the specific visual features present in the current glance of a
scene,
%
2) and connecting that to the stable, high-level knowledge of where the place
exists in the world, what has happened here in the past, and what possible
actions we could take here in the future \citep{baldassano2016two}.
%
For most cognitive and physical tasks we undertake in real-world places, the
specific visual attributes we perceive are just a means to this end, of
recalling and updating information about the physical environment; ``the
essential feature of a landmark is not its design, but the place it holds in a
city’s memory'' [Muschamp, 2006, in New York Times]\citep{baldassano2016two}.

\subsubsection{contextual associations: Baumann 2016}

% visuospatial and mnemonic processes
The PHC plays a key role in both visuospatial analysis of scenes [Epstein et
al., 1999, 2003; Park and Chun, 2009; Rajimehr et al., 2011] and (contextual)
mnemonic processing [Aminoff et al., 2013, Bar and Aminoff, 2003; Düzel et al.,
    2003; Janzen and van Turennout, 2004; Baumann et al., 2010; Wegman and
Janzen, 2011] \citep{baumann2016functional}
% associative processing
The PCH has been implicated in the integration and retrieval of contextual
associations in memory [Aminoff et al., 2013; Bar and Aminoff, 2003; Bar et al.,
2008a, 2008b].

Contextual associations: relations between objects and conditions that describe,
represent, and bring meaning to an environment [Aminoff et al., 2013]
\citep{baumann2016functional}.
%
Examples: objects that commonly co-occur, such as a refrigerator and an oven
(typically in a kitchen) or familiar spatial configurations of objects, (rows of
tables and chairs in a school classroom). According to this view, activity in
the parahippocampal cortex reflects modality-independent retrieval of contextual
information from memory, such as which objects typically occur in a given scene
and where they are likely to be located relative to one another
\citep{baumann2016functional}.

%
However, it has remained unclear whether these two processes are functionally
and anatomically segregated within the parahippocampal cortex
\citep{baumann2016functional}.
%
We provide evidence for a dissociation between neural activation patterns
associated with visuospatial analysis of scenes and contextual mnemonic
processing along the parahippocampal longitudinal axis
\citep{baumann2016functional}.

%
\citep{baumann2016functional} paradigm: We measure parahippocampal responses
while participants engaged in a task that required them to judge the contextual
relatedness of scene and object pairs, which were presented either as words or
pictures \citep{baumann2016functional}.
%
Participants judged the contextual relatedness of scene and object pairs (“bike”
\& “bell” are a contextually congruent object– object pair, “sofa” \&
“microscope” are incongruent; “boat” \& “lake” are a contextually congruent
object–scene pair, “tractor” \& “hotel” are
incongruent)\citep{baumann2016functional}.
%
Each pair was presented either in printed-word format or in a combined
word–picture format. That allowed us to present pictorial objects and scenes in
isolation (Fig. 1)\citep{baumann2016functional}.
%
To identify visuospatial regions of the PHC, we tested for voxels with greater
activity for picture–scene trials than for picture–object trials over and above
activity differences elicited by the comparison of word–scene trials and word–
object trials\citep{baumann2016functional}.
%
Additionally to locate context-related regions of the PHC, we tested for voxels
that were selectively active during the contextual judgment task regardless of
the type of stimulus (scenes vs objects) or presentation modality (word vs
picture)\citep{baumann2016functional}.

%
Results: aPHC is more active during contextual
judgments regardless of stimulus category (scenes vs objects) or modality (word
vs picture).
%
The left aPHC was active in all contextual judgment task conditions. This
suggests a functional segregation, with posterior sections of the PHC supporting
visuospatial processing of scenes and anterior sections of the left PHC involved
in contextual associative processing\citep{baumann2016functional}.
%
It is important to note that, whereas our study only examined retrieval-related
activity for object–object and object–scene relationships, findings from prior
studies suggest that the functions of the aPHC are not limited to these types of
material, but should also be involved in the retrieval of associations involving
other stimulus categories such as faces [Düzel et al., 2003; Kirwan and Stark,
2004]\citep{baumann2016functional}.

%
Interpretation: Activation maxima associated with visuospatial and mnemonic
processes were spatially segregated, providing support for the existence of
functionally distinct subregions along the PHC longitudinal axis and suggesting
that the PHC serves as a functional interface between perception and memory
systems\citep{baumann2016functional}.
%
This anatomical segregation of function [cf. their results] suggests a
predominantly perceptual role for the pPHC and a mnemonic role for the anterior
parahippocampal cortex (Note: the anterior parahippocampal cortex should not be
confused with the anterior portion of the parahippocampal gyrus, which includes
the perirhinal cortex; Ranganath and Ritchey,
2012.)\citep{baumann2016functional}.
%
We suggest that the aPHC encodes incoming information in an amodal format and
acts as an interface with other memory regions, including the hippocampal,
retrosplenial, and perirhinal memory systems (see Ranganath and Ritchey, 2012,
for an review)\citep{baumann2016functional}.
%
Linsley and McEvoy (2015) found (using an fMRI searchlight analysis) that
activity patterns in the aPHC were strongly modulated by the presence of objects
in scenes; patterns in the pPHC were not modulated. This again suggests that the
aPHC is more concerned with contextual than visuospatial analysis of scene
images\citep{baumann2016functional}.

%
Hypothesis: Moreover, it is conceivable that different categories of contextual
associations (e.g., spatial, temporal, affective, etc.) cluster in different
subregions within the aPHC.  High-resolution fMRI and analysis techniques such
as adaptation fMRI [Krekelberg et al., 2006] or multivoxel pattern
classification [Norman et al., 2006] could be used to determine any such
finegrained functional topography within the parahippocampal cortex]

\subsubsection{contextual associations: Aminoff 2013 (review) + 2015}

% memory
Models of recognition memory have previously identified parahippocampal cortex
as primarily encoding spatial context information (Eichenbaum et al., 2007)
\citep{baldassano2013differential}.

% contextual associations in anterior vs. posterior
\citep{aminoff2013role} proposed that the general function of the PHC can be
thought of as processing of contextual associations. Activity within the PHC is
distributed along an anterior–posterior axis:
% pPPA
Activity related to spatial contexts is focused in the posterior part of the PHC
=> posterior subregion of PHC is particularly optimized to process spatially
organized contextual associations.
% aPPA
Activity evoked by non-spatial contexts focused in the more anterior part of the
PHC (optimized to process contextual associations in other, non-spatial domains)
[bar2003cortical, aminoff2007parahippocampal] \citep{aminoff2013role}.

% Aminoff regarding contextual processing in the PHC and beyond
\citep{aminoff2013role} regarding method in [aminoff2007parahippocampal]: we
compared contextual processing of objects that are strongly related to a
specific place (oven is found in a kitchen) with contextual processing of
objects that are highly associated with a context but not a specific place
(birthday cake is found at a birthday party; but the party can take place
anywhere)\citep{aminoff2013role}.
%
Activity elicited by these two types of contextual objects was compared with the
activity elicited for objects that were only weakly associated with many
contexts (e.g., a lamp) \citep{aminoff2013role}.
% results
Differential activity was found in the PHC and the RSC, replicating the previous
findings [Bar \& Aminoff (2003) The parahippocampal\dots]
\citep{aminoff2013role}.

\citep{baumann2016functional} zu \citep{aminoff2015associative}:
% pPHC
pPHC showed increased activity when participants viewed (alrady familiar)
spatial configurations of meaningless shapes (regardless of their individual
identities);
% aPHC
aPHC was more active during the display of (already familiar) meaningless shapes
(regardless of their spatial configuration).
%
These findings can be interpreted as suggestive of pPHC visuospatial processes
and aPHC contextual processes \citep{baumann2016functional}.

\paragraph{Abstract}

\citep{aminoff2015associative} How are complex visual entities such as scenes
represented in the human brain? Along what visual and semantic dimensions are
scenes encoded in memory?
%
One hypothesis: global spatial properties provide a basis for categorizing the
neural response patterns arising from scenes \citep{aminoff2015associative}.
%
In contrast, non-spatial properties, such as single objects, also account for
variance in neural responses\citep{aminoff2015associative}.

%
The list of critical scene dimensions has continued to grow (sometimes in a
contradictory manner), coming to encompass properties such as geometric layout,
big/small, crowded/sparse, and
three-dimensionality\citep{aminoff2015associative}.
%
We demonstrate that these dimensions may be better understood within the more
general framework of associative properties\citep{aminoff2015associative}.
%
Across both the perceptual and semantic domains, features of scene
representations are related to one another through learned
associations\citep{aminoff2015associative}.

%
We investigated whether different types of relations, all falling under the
heading of associative processing, reliably recruit specific components of the
network of brain regions known to be scene
selective\citep{aminoff2015associative}.
%
Critically, the components of such associations are consistent with the
dimensions that are typically invoked to account for scene understanding and its
neural bases\citep{aminoff2015associative}.

Results: We show that non-scene stimuli displaying novel associations across
identities or locations recruit putatively scene-selective regions of the human
brain (the parahippocampal/lingual region, the retrosplenial complex, and the
transverse occipital sulcus/occipital place area)\citep{aminoff2015associative}.
%
Moreover, we find that the voxel-wise neural patterns arising from these
associations are significantly correlated with the neural patterns arising from
everyday scenes providing evidence whether the same encoding principals underlie
both types of processing\citep{aminoff2015associative}.

%
Interpretation: Results provide evidence for the hypothesis that the neural
representation of scenes is better understood within the broader theoretical
framework of associative processing\citep{aminoff2015associative}.
%
Results also demonstrate a division of labor that arises across scene-selective
regions when processing associations and scenes providing better understanding
of the functional roles of each region within the cortical network that mediates
scene processing\citep{aminoff2015associative}.

\paragraph{Intro}

Scenes are complex stimuli containing rich, statistically regular information
about objects, background, context, semantics, and spatial layout at multiple
scales\citep{aminoff2015associative}.
%
As a core component of scene understanding we extract and learn these
regularities (for example, coming to know that certain objects typically appear
together or that certain objects are likely to appear in a given spatial
relationship [1–3])\citep{aminoff2015associative}.
%
Critically, these associated regularities are not only useful in defining scene
categories, but also in predicting which other objects and relations are likely
to occur within a scene [5]\citep{aminoff2015associative}.

% a-modality
Features of any kind of mental representation, irrespective as to whether that
representation is nominally visual, linguistic, etc., are related to one another
via learned associations\citep{aminoff2015associative}.
%
These associations are not necessarily modality-specific (for example, visual
representations are likely to carry many semantic and affective associations not
directly present in the image)\citep{aminoff2015associative}.
%
With respect to scene understanding, we construe contextual associative
processing as a more semantically-driven process in which associations are not
arbitrary relations, but rather relations that emerge as a consequence of their
shared context within the larger scene.
%
Associations are not simply frequently co-occurring features pairs; instead they
are pairs that both co-occur and add meaning to scenes
\citep{aminoff2015associative}.
%
Furthermore, the mechanism by which scenes are perceived, recognized, and
understood, is through means of processing the associations elicited from
components of the scene \citep{aminoff2015associative}.

%
At the core of neurally-based theories of scene perception are the issues of the
computations and representations instantiated in each of these brain regions.
The literature has focused on more on the latter, characterizing the nature of
the information encoded about scenes\citep{aminoff2015associative}.
%
It has been suggested that scenes are analyzed in terms of their spatial global
properties, such as the ‘spatial envelope’, which takes into account a scene’s
overall spatial structure and layout [20,21]\citep{aminoff2015associative}.
%
Empirically, it has been demonstrated that these global properties are salient
cues for categorizing scenes in both behavior [22] and in patterns of neural
activity [23–26]\citep{aminoff2015associative}.
%
Compared to other factors that characterize scenes (i.e., content and
depth), the expanse of the scene (i.e. its spatial boundary) has been found to
be the most effective in accounting for variations in the neural responses
within scene-selective brain regions [23,24]\citep{aminoff2015associative}.
%
Generally, spatial information defining the geometric layout of a scene has
often been implicated in determining the neural responses arising from
scene-selective brain regions [27]\citep{aminoff2015associative}.

%
In contrast, non-spatial properties can account for variations in the neural
responses associated with scene processing and representation\citep{aminoff2015associative}.
%
For example, Harel et al. [11], found that the neural encoding of scenes
captures information about single objects (i.e., non-spatial) as well as
background spatial properties\citep{aminoff2015associative}.
%
Supporting this point, strongly contextualized objects also elicit neural
activity within scene-selective cortex [28,29]\citep{aminoff2015associative}.

%
Finally, objects present as the contents of a scene can also modulate activity
in scene-selective regions\citep{aminoff2015associative}.
%
For example, scenes where the most salient object carries strong contextual
associations (e.g., a scene with a parking meter) recruit scene-selective
regions more than do scenes with a salient object carrying weak contextual asso-
ciations (e.g., a scene with a squirrel) [30]\citep{aminoff2015associative}.
%
Overall, scene-selective brain regions are encoding a rich collection of
information, including global and local properties, spatial background infor-
mation, and individual object tokens\citep{aminoff2015associative}.
